---
title: "Step 9 - CSTARS Vs. MultiSpectral"
author: "cade"
date: "May 30 2018"
output: html_notebook
---
### Description 
Two part script:

1) Extracts stratified random samples from landsat 8 most recently classified file first and then applies to CSTARS classification.

- L8 ---> Hyperspectral/S5
2) Extracts stratified random samples from hypersepctral data and then applies to multispectral datasets

- Hyperspectral ---> L8(x2)/S5(2x)

- This approach is likely more accurate because it uses hyperspectral data as the reference

*List of input files:*


*List of output files:*


#### Load packages 

```{r}
require(data.table)
require(plyr)
require(raster)
require(rgdal)
library(tidyverse)
library(stringr)
library(lubridate)
library(rgeos)
require(caret)

```

#### Step 1: Convert CSTARS Classification to 4 classes

This was completed in ENVI using the post classification toolset and the ROI tool

1) In main envi. Tools -> post classification -> reassign groups 

2) Create ROIS of each area to reassign values --> note masked areas were reassigned with the value 9. EMR = 1, FLT = 2, SAV = 3, water = 1

Follow the instructions on this website;
http://www.harrisgeospatial.com/Support/SelfHelpTools/HelpArticles/HelpArticles-Detail/TabId/2718/ArtMID/10220/ArticleID/18580/How-to-change-the-classification-values-pixel-values-in-an-ENVI-Classic-classification-image.aspx

3) Save as a tiff in ArcMap to ensure can be read into R 

+ The output file is located "E:/cade/Classification_CSTARS/2015/201509_02_63_mosaic_v2_complete_Copy_regrouped_renumbered_arcmap"

**Error:** There was an error when trying to use the extent function in the stratifiedSample tool
therefore all the rasters had to be cropped to the different study areas before values were extracted. For CSTARS classification, it was more computation efficient to crop the rasters by study area using the Extract by Mask tool. 

The output rasters are loocated in:
"E:/cade/Classification_CSTARS/2015" with the subregion name appended to the file name listed above.

#### Step 2: Read in Hyperspectral and Multispectral Classifications

Set directories
```{r}
# set directories for hyperspectral classifcation and multispectral classifcation
hyperDir <-"E:\\cade\\Classification_CSTARS"
multiDir <- "E:/cade/CommEcolProj/Data/MultiRasters"
```

CSTARS Classification
```{r}
# read in shrutis AVIRIS classification
shrutiClass <- raster(paste0(hyperDir,"/2015/201509_02_63_mosaic_v2_complete_Copy_regrouped_renumbered_arcmap.tif"))
NAvalue(shrutiClass) <- 0  

```

MultiSpectral Classification

+ MultiSpectral rasters had to be cropped to waterway mask to ensure stratified sampling was done correctly.

+ Located in 'E:/cade/CommEcolProj/Data/MultiRasters'

+ All were cropped using extract by mask in ArcMap and shruti_waterways_merge.shp

```{r}
# read in the closest multi spectral classifcation image 
# list of raster images
rasterList <- list.files(multiDir, pattern = "*_crop\\.tif$", full.names= T)
```

List of shapefiles for study areas 
```{r}
# need a list of the shape files and to extract the extent below 
shpDir <- "./Data/Vector/DifferentArea_CropBoxes"
shpList <- list.files(shpDir, pattern = "shp$")[c(1,2,5,6,9)]
shpList <- gsub(".shp","", shpList)
shpList
```


#### Step 3: Extract values l8 -> cstars



```{r}
# out  directory for extractions
dirOut <- "./Output/CompareAVIRIS"

# create empty confusion matrix table
cm.all3 <- NULL

# empty count
nCount <- NULL 

# select raster L8 from most recent classification
# ! make this better by not referencing to 2
L8Rast <- raster(rasterList[2]) 

# new raster list
rastCompList <- rasterList[-2]

for (i in 1:length(shpList)){
     # read in shapefile
    subArea <- shpList[i] #i
    shpFile <- readOGR(shpDir, subArea) #i 
    
    # crop raster
    L8RastCrop <- crop(mask(L8Rast,shpFile), shpFile)
    
    # count pixels
    layer.freq <- freq(L8RastCrop, useNA="no")
    n1 <- ceiling(min(layer.freq[,"count"]) * 0.6)
    n2 <- data.frame(subregion = subArea,
                     numberSamples = n1)
    nCount <- rbind(n2,nCount)
    
    
      for(j in 1:length(rastCompList)){
      # read in second raster to sample
      rast <- raster(rastCompList[j]) #j
      NAvalue(rast) <- 0
      
          for(x in 1:100){
          
          # iteration
          iteration = x
        
          rSample <- sampleStratified(L8RastCrop, size = n1, xy = TRUE, sp=TRUE, na.rm = TRUE) 
          
          # count number of pixels
          #plyr::count(as.vector(rSample$L8_20150812_classified_60_Apr29))

          # sample pixels
          # Extract at a lower resolution image
          testExt <- raster::extract(rast, rSample, sp= TRUE) %>% 
            na.omit() 

          # change names of L8 raster in extract table
          names(testExt)[4] <- "L8Class" 
          
          # confusion matrix
          mod_RF_conMatrix <- confusionMatrix(data = testExt[[5]],
                                              reference = testExt$L8Class) 
          mod_RF_conMatrix
          
          # name of the raster that intial raster is being tested against
          rasterName <- names(testExt)[5]
          
          cmFileName <- paste0(dirOut,"\\",rasterName,"_",subArea,"_CMoutputMay30_it",x,".txt")
          
          ## save cm output
          cm <-capture.output(print(mod_RF_conMatrix), file = cmFileName, append = TRUE) 
          
          ## add accuracy to a table use str(cm) to determine what the variables are called
          overall <- mod_RF_conMatrix$overall
          overall.accuracy <- overall['Accuracy']
          ## will compute the accuracy statistics for all
          byC <- mod_RF_conMatrix$byClass
          prod.EMR <- byC['Class: 1','Sensitivity']
          prod.FLT <- byC['Class: 2','Sensitivity']
          prod.SAV <- byC['Class: 3','Sensitivity']
          prod.water <- byC['Class: 4','Sensitivity']
          user.EMR <- byC['Class: 1','Pos Pred Value']
          user.FLT <- byC['Class: 2','Pos Pred Value']
          user.SAV <- byC['Class: 3','Pos Pred Value']   
          user.water <- byC['Class: 4','Pos Pred Value']
          
          cm.all= data.frame(rasterName, subArea, overall.accuracy, prod.EMR, user.EMR,
                             prod.FLT, user.FLT, prod.SAV, user.SAV, prod.water, user.water,
                             row.names= NULL,iteration)
          cm.all3 = rbind(cm.all,cm.all3)
        }
    rm(rast)
    }
  rm(L8RastCrop)
  removeTmpFiles(h=0)
}


write.csv(cm.all3,paste0(dirOut,"\\compareAVIRIScm_L82AVIRISmay30.csv",row.names = F))

```

```{r}
landsatExt <- read_csv(paste0(dirOut,"\\compareAVIRIScm_L82AVIRISmay30.csv"))[-1]
```

```{r}
landAccuracy <- landsatExt %>% 
  as.tibble() %>%
  dplyr::select(-iteration)%>%
  melt() %>% 
  mutate(percentAcc = value*100) %>%
  dplyr::rename(AccuracyType = variable) %>%
  group_by(rasterName, subArea) %>%
  nest()

plotAccuracy <- function(df){
  p <- ggplot(df, aes(x = AccuracyType, y = percentAcc)) + geom_boxplot() + theme_classic()
  p
}

plotResults <- map(landAccuracy$data,plotAccuracy)
plotResults
```

#### Step 4: reverse reference

```{r}
# out  directory for extractions
dirOut <- "./Output/CompareAVIRIS"

# create empty confusion matrix table
cm.all3 <- NULL

# empty count
nCount <- NULL 

# select raster L8 from most recent classification
# ! make this better by not referencing to 2
L8Rast <- raster(rasterList[2]) 

# new raster list
rastCompList <- rasterList[-2]

for (i in 1:length(shpList)){
     # read in shapefile
    subArea <- shpList[i] #i
    shpFile <- readOGR(shpDir, subArea) #i 
    
    # crop raster
    L8RastCrop <- crop(mask(L8Rast,shpFile), shpFile)
    
    # count pixels
    layer.freq <- freq(L8RastCrop, useNA="no")
    n1 <- ceiling(min(layer.freq[,"count"]) * 0.6)
    n2 <- data.frame(subregion = subArea,
                     numberSamples = n1)
    nCount <- rbind(n2,nCount)
    
    
      for(j in 1:length(rastCompList)){
      # read in second raster to sample
      rast <- raster(rastCompList[j]) #j
      NAvalue(rast) <- 0
      
          for(x in 1:100){
          
          # iteration
          iteration = x
        
          rSample <- sampleStratified(L8RastCrop, size = n1, xy = TRUE, sp=TRUE, na.rm = TRUE) 
          
          # count number of pixels
          #plyr::count(as.vector(rSample$L8_20150812_classified_60_Apr29))

          # sample pixels
          # Extract at a lower resolution image
          testExt <- raster::extract(rast, rSample, sp= TRUE) %>% 
            na.omit() 

          # change names of L8 raster in extract table
          names(testExt)[4] <- "L8Class" 
          
          # confusion matrix
          mod_RF_conMatrix <- confusionMatrix(data = testExt$L8Class,
                                              reference = testExt[[5]]) 
          mod_RF_conMatrix
          
          # name of the raster that intial raster is being tested against
          rasterName <- names(testExt)[5]
          
          cmFileName <- paste0(dirOut,"\\",rasterName,"_",subArea,"_CMoutputMay30_it",x,".txt")
          
          ## save cm output
          cm <-capture.output(print(mod_RF_conMatrix), file = cmFileName, append = TRUE) 
          
          ## add accuracy to a table use str(cm) to determine what the variables are called
          overall <- mod_RF_conMatrix$overall
          overall.accuracy <- overall['Accuracy']
          ## will compute the accuracy statistics for all
          byC <- mod_RF_conMatrix$byClass
          prod.EMR <- byC['Class: 1','Sensitivity']
          prod.FLT <- byC['Class: 2','Sensitivity']
          prod.SAV <- byC['Class: 3','Sensitivity']
          prod.water <- byC['Class: 4','Sensitivity']
          user.EMR <- byC['Class: 1','Pos Pred Value']
          user.FLT <- byC['Class: 2','Pos Pred Value']
          user.SAV <- byC['Class: 3','Pos Pred Value']   
          user.water <- byC['Class: 4','Pos Pred Value']
          
          cm.all= data.frame(rasterName, subArea, overall.accuracy, prod.EMR, user.EMR,
                             prod.FLT, user.FLT, prod.SAV, user.SAV, prod.water, user.water,
                             row.names= NULL,iteration)
          cm.all3 = rbind(cm.all,cm.all3)
        }
    rm(rast)
    }
  rm(L8RastCrop)
  removeTmpFiles(h=0)
}
write.csv(cm.all3,paste0(dirOut,"\\compareAVIRIScm_L82AVIRIS_reverseReference_may30.csv"), row.names=F )
```

```{r}
landAccuracyReverse <- read_csv(paste0(dirOut,"\\compareAVIRIScm_L82AVIRIS_reverseReference_may30.csv"))
landAccuracyRev <- landAccuracyReverse %>% 
  as.tibble() %>%
  dplyr::select(-iteration)%>%
  melt() %>% 
  mutate(percentAcc = value*100) %>%
  dplyr::rename(AccuracyType = variable) %>%
  group_by(rasterName, subArea) %>%
  nest()

plotAccuracy <- function(df){
  p <- ggplot(df, aes(x = AccuracyType, y = percentAcc)) + geom_boxplot() + theme_classic()
  p
}

plotResults <- map(landAccuracyRev$data,plotAccuracy)
plotResults
```





#### Step 4: Extract values cstars -> L8
```{r}
cm.all3 <- NULL

shrutiCropList <- list.files(paste0(hyperDir,"/2015"), pattern = "\\.*tif$", full.names = T)[-c(1,7)]
# new raster list
rastCompList <- rasterList[-1]

for (i in 1:length(shrutiCropList)){
  # name sub area
    subArea <- unlist(strsplit(shrutiCropList[i],"[_]")) #i
    subArea <- subArea[length(subArea)]
    
    # crop raster
    shrutiClassCrop <- raster(shrutiCropList[i]) # i
    NAvalue(shrutiClassCrop) <- 0
    
    # count pixels
    # layer.freq <- freq(L8RastCrop, useNA="no")
    # n1 <- ceiling(min(layer.freq[,"count"]) * 0.6)
    # n2 <- data.frame(subregion = subArea,
    #                  numberSamples = n1)
    # nCount <- rbind(n2,nCount)
    
  
    
      for(j in 1:length(rastCompList)){
      # read in second raster to sample
      rast <- raster(rastCompList[j]) #j
      NAvalue(rast) <- 0
      
          for(x in 1:100){
          
          # iteration
          iteration = x
        
          rSample <- sampleStratified(shrutiClassCrop, size = 2000, xy = TRUE, sp=TRUE, na.rm = TRUE) 
          
          # count number of pixels
          #plyr::count(as.vector(rSample$L8_20150812_classified_60_Apr29))

          # sample pixels
          # Extract at a lower resolution image
          testExt <- raster::extract(rast, rSample, sp= TRUE) %>% 
            na.omit() 

          # change names of L8 raster in extract table
          names(testExt)[4] <- "ShrutiClass" 
          
          # confusion matrix
          mod_RF_conMatrix <- confusionMatrix(data = testExt[[5]],
                                              reference = testExt$ShrutiClass) 
          mod_RF_conMatrix
          
          # name of the raster that intial raster is being tested against
          rasterName <- names(testExt)[5]
          
          cmFileName <- paste0(dirOut,"\\",rasterName,"_",subArea,"_CMoutputMay30_aviris_it",x,".txt")
          
          ## save cm output
          cm <-capture.output(print(mod_RF_conMatrix), file = cmFileName, append = TRUE) 
          
          ## add accuracy to a table use str(cm) to determine what the variables are called
          overall <- mod_RF_conMatrix$overall
          overall.accuracy <- overall['Accuracy']
          ## will compute the accuracy statistics for all
          byC <- mod_RF_conMatrix$byClass
          prod.EMR <- byC['Class: 1','Sensitivity']
          prod.FLT <- byC['Class: 2','Sensitivity']
          prod.SAV <- byC['Class: 3','Sensitivity']
          prod.water <- byC['Class: 4','Sensitivity']
          user.EMR <- byC['Class: 1','Pos Pred Value']
          user.FLT <- byC['Class: 2','Pos Pred Value']
          user.SAV <- byC['Class: 3','Pos Pred Value']   
          user.water <- byC['Class: 4','Pos Pred Value']
          
          cm.all= data.frame(rasterName, subArea, overall.accuracy, prod.EMR, user.EMR,
                             prod.FLT, user.FLT, prod.SAV, user.SAV, prod.water, user.water,
                             row.names= NULL,iteration)
          cm.all3 = rbind(cm.all,cm.all3)
        }
    rm(rast)
    }
rm(ShrutiClassCrop)
removeTmpFiles(h=0)
}

```



```{r}

```

